Live Functional Programming with Typed Holes

### 2018-07-10 examples-1.tex
added type inspector to fig2

Let us now consider a second more sophisticated example: an incomplete implementation of the recursive quicksort function, shown in Fig.~\ref{fig:qsort-example-code}. So far, the programmer (perhaps a student, or a lecturer using \Hazel as a presentational aid during class) has filled in the base case, and in the recursive case, has selected the head of the list as the pivot, partitioned the remainder of the list relative to the pivot and made the two recursive calls. A hole appears in the return position of the function body as the programmer contemplates how to combine the available variables.

>>>>

Let us now consider a second more sophisticated example: an incomplete implementation of the recursive quicksort function, shown in Fig.~\ref{fig:qsort-example-code}. So far, the programmer (perhaps a student, or a lecturer using \Hazel as a presentational aid during class) has filled in the base case, and in the recursive case, has selected the head of the list as the pivot, partitioned the remainder of the list relative to the pivot and made the two recursive calls. A hole appears in the return position of the function body as the programmer contemplates how to combine the available variables with an appropriate list expression, as indicated by the type inspector in Fig.~\ref{fig:qsort-type-inspector}.

### 2018-07-10 qsort-example.tex
updates to sec 2
added type inspector to fig2

\begin{figure}[t]
\begin{subfigure}[t]{\textwidth}
\centering
\includegraphics[width=0.55\textwidth,interpolate=false,valign=t]{images/qsort-code.png}
\vspace{-3px}
\caption{The result of evaluating this incomplete quicksort function applied to a test value is a hole closure.}
\label{fig:qsort-example-code}
\end{subfigure}

@@

\caption{Example 2: Incomplete Quicksort}
\label{fig:qsort-cell-mockup}
% \end{subfigure}
\end{figure}

>>>>

\begin{figure}[t]
\begin{subfigure}[t]{0.65\textwidth}
\centering
\includegraphics[width=\textwidth,interpolate=false,valign=t]{images/qsort-code.png}
\caption{The result of evaluation is a hole closure.}
\label{fig:qsort-example-code}
\end{subfigure}
~
\begin{subfigure}[t]{0.33\textwidth}
\centering
\includegraphics[width=\textwidth,interpolate=false,valign=t]{images/type-inspector.png}
\vspace{-2px}
\caption{The type inspector
continuously provides static information about the expression at the cursor. Here, it tells us that the hole at the cursor should be filled by a list expression. Holes have hole (i.e. unknown) type.
}
\label{fig:qsort-type-inspector}
\end{subfigure}

@@

\caption{Example 2: Incomplete Quicksort}
\label{fig:qsort-cell-mockup}
% \end{subfigure}

\vspace{-6px}
\end{figure}
